\vspace{-2cm} Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of G dwarfs \vspace{-0.5cm}

### 2017-06-26 paper/ms.tex
minor tweaks (mostly latex quirks)

% ------------------------
% nature summary paragraph
% ------------------------
% - a fully referenced paragraph, ideally of about 200 words, but certainly no
%   more than 300 words, aimed at readers in other disciplines.
% - This paragraph starts with a 2-3 sentence basic introduction to the field;
%   followed by a one-sentence statement of the main conclusions starting 'Here
%   we show' or equivalent phrase; and finally, 2-3 sentences putting the main
%   findings into general context so it is clear how the results described in
%   the paper have moved the field forwards.
% - annotated example: https://www.nature.com/nature/authors/gta/2c_Summary_para.pdf
% ------------------------
\section{Summary}
{\bf \noindent
  Stars that are born together are expected to have the same chemical
  compositions initially.
  Detailed chemical abundance studies of stars in wide binaries indeed reveal
  little to no abundance differences in most
  cases\citep{Gratton:2001aa,Desidera:2004aa}.
  However, the formation and evolution of different planetary systems around
  each star in a wide binary may eventually lead to differences in the chemical
  abundances of the component stars' radiative and convective
  layers\cite{Pinsonneault:2001aa,Chambers:2010aa}.
  Wide binary systems of two twin-like stars are particularly useful since such
  chemical signature may be more easily detectable as abundance differences,
  free from dependences on stellar parameters or confusion with Galactic
  chemical evolution.
  A handful of wide binaries that show small differences ($0.03$--$0.1$~dex)
  in their surface chemical abundances have been reported so far
  \cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,Teske:2013aa,
    Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa},
  however, a conclusive example of planetary accretion has not yet been found.
  %
  Here we report the discovery of a comoving pair of bright, sun-like
  stars---HD~240430 and HD~240429, hereafter ``\bizarreone'' and
  ``\sunanalog''--- with significant differences ($\approx 0.2$~dex) in their
  chemical abundances that strongly suggests accretion of a massive rocky
  planetary system in one of the stars within the last billion years.
  The more metal-rich of the two, \bizarreone, shows an enhancement of refractory
  elements by $\approx 0.2$~dex and a small enhancement ($\lesssim 0.11$~dex) of
  (moderately) volatile elements.
  The two stars also show high \elem{Li} abundance given their age of $\sim 4$ Gyr,
  as inferred from their stellar parameters.
  We suggest that the star \bizarreone recently accreted
  $\approx 15$~\mearth\ of rocky material, selectively enhancing the
  refractory elements in its surface and convective envelope.
  The other star, \sunanalog, may also have had a similar accretion
  event given its high surface \elem{Li} abundance but of much smaller amount
  ($\approx 4$~\mearth).
  This pair of stars provides evidence that dynamical accretion of rocky planets
  does happen during the lifetime of sun-like stars.
}

@@

\item [c] Absolute abundances from Myles \etal (in prep.).

@@

% general description of the pair and measurements
\sunanalog\ and \bizarreone\ were identified as a candidate comoving star pair
in our recent search for comoving stars using the proper motions and parallaxes
from the {\it Tycho-Gaia Astrometric Solution} catalog (hereafter \tgas), a
component of the first data release of the astrometric space mission \gaia\cite{2016A&A...595A...2G}
(the astrometric measurements are listed in \tablename~\ref{tab:t1}).
The pair has also been previously recognized as a visual double star system
in the Washington Double Star catalog\cite{2001AJ....122.3466M}.
The two stars have spectral types G0 and G2, both similar to the Sun (G2).
In a separate effort to study the detailed chemical abundances of potential
planet-hosting stars, high resolution ($R=\lambda/\Delta\lambda\approx 70000$),
high signal-to-noise ratio (typically $>200$ per pixel in continuum) spectra of
both stars for the wavelength range $5164$--$7799$~\AA were obtained using the
HIRES spectrograph on the Keck-I telescope\cite{2016ApJS..225...32B}.
The resulting measurements include elemental abundances for 15 chemical species
(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar
parameters and high precision ($\sigma\approx0.2$~\kms) radial velocities
(section~Table~\ref{tab:t1}).

@@

% novelty
The observed difference in metallicity and abundances are genuinely rare and
unexpected.
None of the other four twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K), wide-binary pairs examined using spectra of similar quality and the same
consistent measurement pipeline shows discrepancies in abundances between the
stars at this level\cite{2016ApJS..225...32B} (\figname~\ref{fig:deltaXH}).
The maximum metallicity difference observed in the other pairs is $\Delta\feh =
0.03$~dex with $1\sigma$ statistical uncertainties in \feh\ of $0.01$~dex.
This is consistent with similar studies of metallicity and abundance
differences in wide binaries\cite{Gratton:2001aa,Desidera:2004aa}.
In fact, the abundance pattern of \bizarreone\ is very unusual
for a star that is enhanced in \feh\ by $0.2$~dex relative to \sunanalog\
($\feh\approx 0$; \figname~\ref{fig:deltaXH}),
implying that a scenario involving Galactic chemical evolution is not plausible
even if we ignore the coeval comparison star, \sunanalog.
The difference of $\approx 0.2$~dex is also the largest among a handful of wide
binaries that do show metallicity and abundance differences with varying
significance\cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,
  Teske:2013aa,Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa}
(\figname~\ref{fig:relabun_tcrank}).

@@

We estimate that the accretion of $\approx 15$~\mearth\ of rocky planets
in \bizarreone\ relative to \sunanalog\ can explain the enhancement in
refractory elements as well as the surface Li abundance.
Because the anchor star, \sunanalog,
is very similar to the Sun in its stellar properties (\teff, \logg, \feh, age),
we can use assume the Sun's photosphere abundances\cite{Asplund:2009aa} as the
pre-accretion state of \bizarreone.
In \figname~\ref{fig:deltaxh_tcrank}, we show the expected change in solar abundances,
$\Delta\elemH{X}$, after adding $15$~\mearth\ of bulk Earth composition
material\cite{2003TrGeo...2..547M} assuming that 2\% of the star's mass is in
its convective zone\cite{Pinsonneault:2001aa}.
It has long been known that more volatile (low \Tcondens) elements are more
depleted in the Earth relative to CI or other carbonaceous
chondrites\cite{mcdonough2001composition} that are thought to reflect the
elemental composition of the pre-solar nebula. \todo{Check end of last sentence}
This trend is presumed to be closely related to the formation of terrestrial
planets and, in particular to the radial temperature gradient in a
protoplanetary disk.
The trend resulting from adding $15$~\mearth\ of bulk Earth provides an overall
good match to the observed $\Delta\elemH{X}$, suggesting that the
refractory-enhanced star, \bizarreone\, accreted $\approx 15$~\mearth\ more of
rocky planetary material than \sunanalog.

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{spec2.pdf}
  \caption{Same as \figname~\ref{fig:spec1}
    but for smaller portions of spectra at longer wavelengths that are
    not dominated by \elem{Fe}.
    We mark elements that give rise to strong absorption lines.
    The feature in the third column of the second row is a strong \elem{Li}
    line that was studied separately in Myles \etal (in prep.).
    Note that the lines of \elem{Na} and \elem{O}, which are under-enhanced
    in \bizarreone\ relative to \elem{Fe} or other refractory elements,
    show noticeably weaker residuals compared to neighboring lines of
    refractory elements.
  }
  \label{fig:spec2}
\end{figure}

>>>>

% ------------------------
% nature summary paragraph
% ------------------------
% - a fully referenced paragraph, ideally of about 200 words, but certainly no
%   more than 300 words, aimed at readers in other disciplines.
% - This paragraph starts with a 2-3 sentence basic introduction to the field;
%   followed by a one-sentence statement of the main conclusions starting 'Here
%   we show' or equivalent phrase; and finally, 2-3 sentences putting the main
%   findings into general context so it is clear how the results described in
%   the paper have moved the field forwards.
% - annotated example: https://www.nature.com/nature/authors/gta/2c_Summary_para.pdf
% ------------------------
\section{Summary}
{\bf \noindent
  Stars that are born together are expected to have the same chemical
  compositions initially.
  Detailed chemical abundance studies of stars in wide binaries indeed reveal
  little to no abundance differences in most
  cases\citep{Gratton:2001aa,Desidera:2004aa}.
  However, the formation and evolution of different planetary systems around
  each star in a wide binary may eventually lead to differences in the chemical
  abundances of the component stars' radiative and convective
  layers\cite{Pinsonneault:2001aa,Chambers:2010aa}.
  Wide binary systems of two twin-like stars are particularly useful since such
  chemical signature may be more easily detectable as abundance differences,
  free from dependences on stellar parameters or confusion with Galactic
  chemical evolution.
  A handful of wide binaries that show small differences ($0.03$--$0.1$~dex)
  in their surface chemical abundances have been reported so far
  \cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,Teske:2013aa,
    Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa},
  however, a conclusive example of planetary accretion has not yet been found.
  %
  Here we report the discovery of a comoving pair of bright, sun-like
  stars---HD~240430 and HD~240429, hereafter ``\bizarreone'' and
  ``\sunanalog''--- with significant differences ($\approx 0.2$~dex) in their
  chemical abundances that strongly suggest accretion of a massive rocky
  planetary system in one of the stars within the last billion years.
  The more metal-rich of the two, \bizarreone, shows an enhancement of refractory
  elements by $\approx 0.2$~dex and a small enhancement ($\lesssim 0.11$~dex) of
  (moderately) volatile elements.
  The two stars also show high \elem{Li} abundance given their age of $\sim 4$ Gyr,
  as inferred from their stellar parameters.
  We suggest that the star \bizarreone\ recently accreted
  $\approx 15$~\mearth\ of rocky material, selectively enhancing the
  refractory elements in its surface and convective envelope.
  The other star, \sunanalog, may also have had a similar accretion
  event given its high surface \elem{Li} abundance but of much smaller amount
  ($\approx 4$~\mearth).
  This pair of stars provides evidence that dynamical accretion of rocky planets
  does happen during the lifetime of sun-like stars.
}

@@

\item [c] Absolute abundances from Myles \etal\ (in prep.).

@@

% general description of the pair and measurements
\sunanalog\ and \bizarreone\ were identified as a candidate comoving star pair
in our recent search for comoving stars using the proper motions and parallaxes
from the {\it Tycho-Gaia Astrometric Solution} catalog (hereafter \tgas), a
component of the first data release of the astrometric space mission \gaia\cite{2016A&A...595A...2G}
(the astrometric measurements are listed in \tablename~\ref{tab:t1}).
The pair has also been previously recognized as a visual double star system
in the Washington Double Star catalog\cite{2001AJ....122.3466M}.
The two stars have spectral types G0 and G2, both similar to the Sun (G2).
In a separate effort to study the detailed chemical abundances of potential
planet-hosting stars, high resolution ($R=\lambda/\Delta\lambda\approx 70000$),
high signal-to-noise ratio (typically $>200$ per pixel in continuum) spectra of
both stars for the wavelength range $5164$--$7799$~\AA\ were obtained using the
HIRES spectrograph on the Keck-I telescope\cite{2016ApJS..225...32B}.
The resulting measurements include elemental abundances for 15 chemical species
(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar
parameters and high precision ($\sigma\approx0.2$~\kms) radial velocities
(section~Table~\ref{tab:t1}).

@@

% novelty
The observed difference in metallicity and abundances are genuinely rare and
unexpected.
None of the other four twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K)
wide-binary pairs examined using spectra of similar quality and the same
consistent measurement pipeline shows discrepancies in abundances between the
stars at this level\cite{2016ApJS..225...32B} (\figname~\ref{fig:deltaXH}).
The maximum metallicity difference observed in the other pairs is $\Delta\feh =
0.03$~dex with $1\sigma$ statistical uncertainties in \feh\ of $0.01$~dex.
This is consistent with similar studies of metallicity and abundance
differences in wide binaries\cite{Gratton:2001aa,Desidera:2004aa}.
In fact, the abundance pattern of \bizarreone\ is very unusual
for a star that is enhanced in \feh\ by $0.2$~dex relative to \sunanalog\
($\feh\approx 0$; \figname~\ref{fig:deltaXH}),
implying that a scenario involving Galactic chemical evolution is not plausible
even if we ignore the coeval comparison star, \sunanalog.
The difference of $\approx 0.2$~dex is also the largest among a handful of wide
binaries that do show metallicity and abundance differences with varying
significance\cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,
  Teske:2013aa,Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa}
(\figname~\ref{fig:relabun_tcrank}).

@@

We estimate that the accretion of $\approx 15$~\mearth\ of rocky planets
in \bizarreone\ relative to \sunanalog\ can explain the enhancement in
refractory elements as well as the surface Li abundance.
Because the anchor star, \sunanalog,
is very similar to the Sun in its stellar properties (\teff, \logg, \feh, age),
we can use assume the Sun's photosphere abundances\cite{Asplund:2009aa} as the
pre-accretion state of \bizarreone.
In \figname~\ref{fig:deltaxh_tcrank}, we show the expected change in solar abundances,
$\Delta\elemH{X}$, after adding $15$~\mearth\ of bulk Earth composition
material\cite{2003TrGeo...2..547M} assuming that 2\% of the star's mass is in
its convective zone\cite{Pinsonneault:2001aa}.
It has long been known that more volatile (low \Tcondens) elements are more
depleted in the Earth relative to CI or other carbonaceous
chondrites\cite{mcdonough2001composition} that are thought to reflect the
elemental composition of the proto-solar nebula. \todo{Check end of last sentence}
This trend is presumed to be closely related to the formation of terrestrial
planets and, in particular to the radial temperature gradient in a
protoplanetary disk.
The trend resulting from adding $15$~\mearth\ of bulk Earth provides an overall
good match to the observed $\Delta\elemH{X}$, suggesting that the
refractory-enhanced star, \bizarreone\, accreted $\approx 15$~\mearth\ more of
rocky planetary material than \sunanalog.

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{spec2.pdf}
  \caption{Same as \figname~\ref{fig:spec1}
    but for smaller portions of spectra at longer wavelengths that are
    not dominated by \elem{Fe}.
    We mark elements that give rise to strong absorption lines.
    The feature in the third column of the second row is a strong \elem{Li}
    line that was studied separately in Myles \etal\ (in prep.).
    Note that the lines of \elem{Na} and \elem{O}, which are under-enhanced
    in \bizarreone\ relative to \elem{Fe} or other refractory elements,
    show noticeably weaker residuals compared to neighboring lines of
    refractory elements.
  }
  \label{fig:spec2}
\end{figure}
